---
title: "Copilot Intro"
author: "Paule Mathieu"
date: "2026-05-28"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction ##
In this document, we will explore the capabilities of Copilot, an AI-powered code assistant developed by OpenAI. Copilot is designed to help developers write code more efficiently by providing suggestions and completing code snippets based on the context of the project.

# Preparing your workspace ##

```{r}
# Load tidyverse and palmerpenguins libraries
library(tidyverse)
#install.packages("palmerpenguins")
library(palmerpenguins)
```

# Prompt for a multi-variable scatter plot ##

```{r}
#create a ggplt scatter plot using the penguins dataset.
#Plot bill_length_mm on the x-axis and bill_depth_mm on the y-axis.
#Color the points by species and use geom_point with size 3.
#Add a minimal theme and lean labels.

ggplot(penguins, aes(x = bill_length_mm, y = bill_depth_mm, color = species)) +
  geom_point(size = 3) +
  theme_minimal() +
  labs(title = "Scatter Plot of Bill Length vs Bill Depth",
       x = "Bill Length (mm)",
       y = "Bill Depth (mm)",
       color = "Species")
```

# Open-ended comparative plotting ##

```{r}
#Generate a scatter plot mapping body_mass_g on the x-axis and flipper_length_mm on the y-axis.
#Add a linear regression trend line (geom_smooth) for each individual species.

ggplot(penguins, aes(x = body_mass_g, y = flipper_length_mm, color = species)) +
  geom_point(size = 3) +
  geom_smooth(method = "lm", se = FALSE) +
  theme_minimal() +
  labs(title = "Scatter Plot of Body Mass vs Flipper Length",
       x = "Body Mass (g)",
       y = "Flipper Length (mm)",
       color = "Species")
```


